---
title: "Readme"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

# KoriPlots

KoriPlots is an R package providing themes that help you make beautiful graphs with ggplot2. KoriPlots contains one main function called `koriPlot()`. Main arguments are:

- `base_size`: Numeric value which defines base font size, given in pts. Default is 16.
- `base_family`: Character string which defines base font family.
- `base_line_size`: Numeric value that defines base size for line elements. Default is base_size/50.
- `base_rect_size`: Numeric value that defines base size for rect elements. Default is base_size/50.
- `base_rect_size`: Numeric value that defines base size for rect elements. Default is base_size/50.
- `grid_lines`: Character value that defines on which axis the grid lines appear. Default is both axes.
- `legend`: Character value that defines on where the legend is placed ("none", "bottom", "top", "left" or "right"). Default is "right".

## Installation

The easiest way to get KoriPlots is to install it from this repo:

```{r, echo = TRUE, message = FALSE, eval = FALSE}
# install.packages("devtools")
devtools::install_github("alfell/KoriPlots")
```

## Version
To check your version of KoriPlots, run:
```{r, echo = TRUE, message = FALSE, eval = FALSE}
packageVersion("KoriPlots")
```

## Examples
```{r, echo = TRUE, message = FALSE}
# Load Package
library(KoriPlots)

# Make Plot (default no grid_lines and legend = "right")
ggplot(data = mtcars,
       aes(x = mpg, 
           y = disp, 
           color = as.factor(cyl))) +
  geom_point() +
  koriPlot()

# Make Plot (grid_lines = "x")
ggplot(data = mtcars,
       aes(x = mpg, 
           y = disp)) +
  geom_point() +
  koriPlot(grid_lines = "x")

# Make Plot (grid_lines = "y", legend = "bottom")
ggplot(data = mtcars,
       aes(x = mpg, 
           y = disp, 
           color = as.factor(cyl))) +
  geom_point() +
  facet_wrap(~carb, 
             ncol = 3) +
  koriPlot(grid_lines = "y",
           legend = "bottom")
```

## Getting Help
If you encounter a bug, please contact the author.

